---
title: "Tutorial 11 - Data Storytelling with Visualization"
author: "Tey Yi Jie"
date: "1/15/2022"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

# Data Preparation

```{r}
#Installing packages
library(tidyverse)
library(circlize)
library(readxl)
```

```{r}
#Getting data
data <- read_excel("~/WQD7001/Data Storytelling/Data-Storytelling-with-Chord-Diagram/BusiestAirlines.xlsx")
data
```

```{r}
#Extract top 10
ndata <- data %>% top_n(10)
ndata
```

```{r}
#Data transformation - Change passengers value to millions
ndata$Passengers <- round(ndata$Passengers /1000000)
ndata
```
# Data Visualization

```{r}
#Chord diagram
chordDiagram(ndata)
```

# Data Storytelling
The chord diagram shows the top 10 busiest airline routes in 2018. The great majority of the origins are Tokyo, Jeju, Sydney, Mumbai, Hanoi, Beijing, Hong Kong and Jakarta. Obviously, the most busiest aiport is Tokyo. It flies to 3 destinations which are Sapporo, Fukuoka and Naha. However, the most busiest airline route is from Jeju to Seoul. In addition, we can say that most of them are domestic flights. This might be due to the low fare of domestic flights if compared to international flights. 

# References
https://en.wikipedia.org/wiki/List_of_busiest_passenger_air_routes

https://methods.sagepub.com/base/download/DatasetHowToGuide/chord-diagram-in-routesonline-2019